\begin{thebibliography}{30}
\bibitem{firstmcts}
Rémi Coulom. 2006. Efficient selectivity and backup operators in Monte-Carlo tree search. In Proceedings of the 5th international conference on Computers and games (CG'06), H. Jaap Van Den Herik, Paolo Ciancarini, and H. H. L. M. Donkers (Eds.). Springer-Verlag, Berlin, Heidelberg, 72-83.

\bibitem{bouzy}
Bruno Bouzy. Associating shallow and selective global tree search with Monte Carlo for 9 x 9 Go. In H. J. van den Herik, Y. Björnsson, and N. S. Netanyahu, editors, Fourth International Conference on Computers and Games, Ramat-Gan,
Israel, 2004.

\bibitem{juille}
Hugues Juillé. Methods for Statistical Inference: Extending the Evolutionary Computation Paradigm. PhD thesis, Brandeis University, Department of Computer Science, May 1999.

\bibitem{mdpchang}
Hyeong Soo Chang, Michael C. Fu, Jiaqiao Hu, and Steven I. Marcus. An adaptive sampling algorithm for solving Markov decision processes. Operations Research, 53(1):126-139, Jan.-Feb. 2005.

\bibitem{mdpperet}
Laurent Péret and Frédérick Garcia. On-line search for solving large Markov decision processes. In Proceedings of the 16th European Conference on Artificial Intelligence, Valence, Spain, August 2004.

\bibitem{uct}
Levente Kocsis and Csaba Szepesvári. 2006. Bandit based monte-carlo planning. In Proceedings of the 17th European conference on Machine Learning (ECML'06), Johannes Fürnkranz, Tobias Scheffer, and Myra Spiliopoulou (Eds.). Springer-Verlag, Berlin, Heidelberg, 282-293. 

\bibitem{alphago}
Silver, David \& Huang, Aja \& Maddison, Christopher \& Guez, Arthur \& Sifre, Laurent \& van den Driessche, George \& Schrittwieser, Julian \& Antonoglou, Ioannis \& Panneershelvam, Veda \& Lanctot, Marc \& Dieleman, Sander \& Grewe, Dominik \& Nham, John \& Kalchbrenner, Nal \& Sutskever, Ilya \& Lillicrap, Timothy \& Leach, Madeleine \& Kavukcuoglu, Koray \& Graepel, Thore \& Hassabis, Demis. (2016). Mastering the game of Go with deep neural networks and tree search. Nature. 529. 484-489. 10.1038/nature16961. 

\bibitem{alphagozero}
Silver, David \& Schrittwieser, Julian \& Simonyan, Karen \& Antonoglou, Ioannis \& Huang, Aja \& Guez, Arthur \& Hubert, Thomas \& Baker, Lucas \& Lai, Matthew \& Bolton, Adrian \& Chen, Yutian \& Lillicrap, Timothy \& Hui, Fan \& Sifre, Laurent \& van den Driessche, George \& Graepel, Thore \& Hassabis, Demis. (2017). Mastering the game of Go without human knowledge. Nature. 550. 354-359. 10.1038/nature24270.

\bibitem{spmcts}
Maarten P. D. Schadd, Mark H. M. Winands, Mandy J. W. Tak, and Jos W. H. M. Uiterwijk. 2012. Single-player Monte-Carlo tree search for SameGame. Know.-Based Syst. 34 (October 2012), 3-11.

\bibitem{hgsts}
Edelkamp, S., Kissmann, P., Messerschmidt, H., \& Sulewski, D. (2010). Finding the Needle in the Haystack with Heuristically Guided Swarm Tree Search. MKWI.

\bibitem{nmcs}
Tristan Cazenave. 2009. Nested Monte-Carlo search. In Proceedings of the 21st international jont conference on Artifical intelligence (IJCAI'09), Hiroaki Kitano (Ed.). Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 456-461.

\bibitem{nrpa}
C. D. Rosin. Nested rollout policy adaptation for Monte Carlo tree search. in Proc. 22nd Int. Joint Conf. Artif. Intell., Barcelona, Spain,
2011, pp. 649-654.

\bibitem{bestcriteria}
Frederik Christiaan Schadd. Monte-carlo search techniques in the mod-
ern board game thurn and taxis. M. sc, Maastricht University, Nether-
lands, 2009.

\bibitem{bestcriteriafoundation}
Chaslot, Guillaume \& Winands, Mark \& Herik, H \& Uiterwijk, Jos \& Bouzy, Bruno. (2008). Progressive Strategies for Monte-Carlo Tree Search. New Mathematics and Natural Computation. 04. 343-357. 10.1142/S1793005708001094. 

\bibitem{uctoptimality}
Kocsis, L., Szepesvári, C., \& Willemson, J. (2006). Improved Monte-Carlo Search.

\bibitem{parallelmcts}
Guillaume M. Chaslot, Mark H. Winands, and H. Jaap Herik. 2008. Parallel Monte-Carlo Tree Search. In Proceedings of the 6th international conference on Computers and Games (CG '08), H. Jaap Herik, Xinhe Xu, Zongmin Ma, and Mark H. Winands (Eds.). Springer-Verlag, Berlin, Heidelberg, 60-71.

\bibitem{cem}
Rubinstein, R. Y., 2003. The Cross-Entropy Method for Combinatorial and Con-
tinuous Optimization. Methodology and Computing in Applied Probability
1 (2), 127–190.

\bibitem{sokobancomplexity}
Joe Culberson. Sokoban is pspace-complete. Technical Report TR 97-02, Dept. of Computing Science, University of Alberta, 1997.

\bibitem{MCTSsurvey}
C. B. Browne, E. Powley, D. Whitehouse, S. M. Lucas, P. I. Cowling, P. Rohlfshagen, S. Tavener, D. Perez, S. Samothrakis and S. Colton, "A Survey of Monte Carlo Tree Search Methods", IEEE Transactions on Computational Intelligence and AI in Games, Vol.4, NO. 1, (2012).

\bibitem{UCB1-Tuned}
P. Auer, N. Cesa-Bianchi and P. Fisher, "Finite-time analysis of the multiarmed bandit problem", Machine Learning, Vol.47, NO. 2, pp. 235-256, (2002).

\bibitem{AMAF}
D. P. Helmbold, and A. Parker-Wood, "All-moves-as-first heuristics in Monte-Carlo Go", in Proc. Int. Conf. Artif. Intell, Las Vegas, NV, pp. 605-610, (2009).

\bibitem{MemoryBounds}
E. J. Powley, P. I. Cowling and D. Whitehouse, "Memory Bounded Monte Carlo Tree Search", Proceedings, The Thirteenth AAAI Conference on
Artificial Intelligence and Interactive Digital Entertainment (AIIDE-17), (2017).

\bibitem{samegamehighscores}
JS-Games.de SameGame - Highscores Retrieved from http://www.js-games.de/eng/highscores/samegame/lx

\bibitem{astar}
Hart, P. E., Nielson, N. J., Raphael, B., 1968. A Formal Basis for the Heuris-
tic Determination of Minimum Cost Paths. IEEE Transactions on Systems
Science and Cybernatics SSC–4 (2), 100–107.

\bibitem{idastar}
Korf, R. E., 1985. Depth-First Iterative Deepening: An Optimal Admissible
Tree Search. Artificial Intelligence 27 (1), 97–109.

\bibitem{24-puzzle}
Korf, R.E., \& Taylor, L.A. (1996). Finding Optimal Solutions to the Twenty-Four Puzzle. AAAI/IAAI, Vol. 2.

\bibitem{transpositiontables}
D. Breuker. Memory versus Search in Games. PhD thesis, University of Maastrciht, Computer Science Department, Maasticht, 1998.

\bibitem{rollingstone}
Andreas Junghanns. Pushing the Limits: New Developments in Single-Agent Search. PhD Thesis, University of Alberta, Department of Computing Science, 1999.

\bibitem{puzzlegames}
G. Kendall, A. Parkes and K. Spoerer, "A survey of NP-Complete puzzles", ICGA Journal, (2008).

\bibitem{enhancedidastar}
A. Reinefeld and T. A. Marsland. 1994. Enhanced Iterative-Deepening Search. IEEE Trans. Pattern Anal. Mach. Intell. 16, 7 (July 1994), 701-710. 

\bibitem{UCTconstant}
A. Reinefeld and T. A. Marsland. 1994. Enhanced Iterative-Deepening Search. IEEE Trans. Pattern Anal. Mach. Intell. 16, 7 (July 1994), 701-710.

\end{thebibliography}

